\documentclass[11pt,a4paper]{article}
\input{preamble}

\newif\ifshowkeywords
\showkeywordstrue

\cvname{Yosr Ben Nagra}
\cvrole{Full-Stack Developer}
\cvcontact{Sokra, Ariana, Tunisia}
\cvphone{+216 53916040}
\cvemail{yosrbennagra@gmail.com}
\cvaddress{Sokra, Ariana, Tunisia}
\cvgithub{https://github.com/YosrBennagra}
\cvsummary{Computer Science Engineering student experienced in full-stack development, AI integration, and DevOps practices. Delivered scalable web platforms, real-time collaboration features, and automation tools across multiple internships. Strong foundation in JavaScript/TypeScript (React, NestJS), Java/Spring Boot, and Python with a focus on clean architecture, testing, and continuous delivery.}

\begin{document}
% ================= HEADER =================
\makecvheader
\makecontactinfo

\CVSummary
% ================= EDUCATION (MOVED UP) =================
\cvsection{Education}
\textbf{Web and Internet technology}\\[-2pt]
Private Higher School of Engineering and Technology (ESPRIT)\\[-2pt]
{\footnotesize\textit{09/2020 - 10/2025}} \hfill {\footnotesize\textit{Tunis, Tunisia}}\\[4pt]


% ================= CORE SKILLS =================
\cvsection{Skills}
\small\textbf{Frontend:} HTML5, CSS3, React.js \;|\; \textbf{Backend:} Node.js, NestJS, Flask, Spring Boot, REST APIs \;|\; \textbf{Programming:} JavaScript, TypeScript, Java, Python \;|\; \textbf{Databases:} SQL (schema design/optimization), MongoDB \;|\; \textbf{DevOps:} Git, CI/CD, Docker, Jenkins (exposure) \;|\; \textbf{Practices:} Agile, Clean architecture, Testing (unit/integration) \;|\; \textbf{Soft Skills:} Problem-solving, Team collaboration, Continuous learning\normalsize

% ================= INTERNSHIPS =================
\cvsection{Internships}

\begin{internship}{Full-Stack Developer Intern (End-of-Studies Internship)}{ITServ}{Tunisia}{Feb 2025 -- Aug 2025}{ITServ is a consulting and service company specializing in ICT and software engineering.}
  \item Designed and developed a full-stack web platform integrating AI, DevOps, and Retrieval-Augmented Generation (RAG).
  \item Implemented an AI-powered symptom checker, blog for doctors, patient forum, and admin dashboard with an AI RAG pipeline.
  \item Applied DevOps practices (CI/CD, containerization, monitoring) and fine-tuned an AI model on medical datasets for improved diagnostic accuracy.
  \item Tech stack: ReactJS, NestJS, MongoDB, Python, Hugging Face, Docker, Jenkins.
\end{internship}

\begin{internship}{Full-Stack Developer Intern}{IronByte}{Tunisia}{Jun 2024 -- Aug 2024}{IronByte is specialized in the development of SaaS applications, and it's a small startup based in Tunisia.}
  \item Developed a web application for an educational institution enabling students to submit assignments and teachers to share lessons.
  \item Built features using NestJS, ReactJS, MongoDB, TypeScript, and JavaScript; added timetable creation tool improving scheduling efficiency.
\end{internship}

\begin{internship}{Full-Stack Developer Intern}{Ooredoo Tunisie}{Tunisia}{Jul 2023 -- Sep 2023}{}
  \item Built an internal communication application with real-time chat, filtering, and search to streamline team collaboration.
  \item Developed front-end and back-end components using Spring Boot and Angular; added unit and integration tests for reliability.
\end{internship}

\begin{internship}{Software Engineer Intern}{ITServ}{Tunisia}{Jul 2021 -- Sep 2021}{ITServ is a consulting and service company specializing in ICT and software engineering.}
  \item Developed an automated code generation tool in Java.
  \item Implemented PDF and Excel to XML conversion to streamline data processing.
  \item Worked with Java and Eclipse IDE.
\end{internship}

% ================= CERTIFICATIONS =================
% (Section removed / not used currently)
% ================= LANGUAGES =================
\cvsection{Languages}
Arabic (Native), English (Fluent professional), French (Fluent professional)

% ================== END DOCUMENT ==================
\end{document}
