\documentclass[11pt,a4paper]{article}
\input{../preamble}

\begin{document}

% Header
\begin{center}
{\Large \textbf{Yosr Ben Nagra}}\\[4pt]
Ariana, Tunisia\\
+216 53916040 | yosrbennagra@gmail.com | github.com/YosrBennagra
\end{center}

\vspace{12pt}

\noindent
Hiring Manager\\
Spot \& Tango\\
Midtown Manhattan, New York

\vspace{10pt}

\noindent
\today

\vspace{10pt}

\noindent
Dear Hiring Manager,

\vspace{8pt}

I am writing to express my strong interest in the Jr. Software Engineer position at Spot \& Tango. As a recent Engineering graduate with hands-on experience building scalable web applications using React, TypeScript, and modern JavaScript frameworks, I am excited about the opportunity to help make every dog healthier while working with a high-growth, mission-driven startup.

What draws me to Spot \& Tango is your commitment to innovation in pet wellness combined with a fast-paced engineering culture. The chance to work on products that directly impact pet health, while thinking about dogs all day, is incredibly motivating.

My technical experience aligns well with your needs. At IronByte, I developed a full-stack educational web application using React, TypeScript, NestJS, and MongoDB, building modular, reusable components and implementing features from design through deployment. I wrote comprehensive integration tests using Jest and collaborated closely with cross-functional teams to deliver business goals.

At IT Serv, I built a web platform with React frontend and Python Flask backend, implementing REST API integrations and optimizing for performance and responsiveness. I also have experience with SQL databases (PostgreSQL, MySQL) and have worked extensively with Git for version control and code reviews.

While I have strong React and TypeScript foundations, I am eager to apply these skills to NextJS and e-commerce platforms like Shopify. I am a quick learner who thrives in startup environments. I understand the pace, the need for simple solutions to complex problems, and the importance of shipping quality code quickly.

I bring strong proficiency in React, TypeScript, JavaScript, HTML5, and CSS3, along with experience in Python, Django, and SQL databases. I have a solid understanding of REST APIs, third-party integrations, and responsive design. I am able to work independently and collaboratively, with excellent problem-solving skills and attention to detail. I am passionate about clean code and creating exceptional user experiences.

I am excited about the prospect of contributing to Spot \& Tango's growth, scaling your products, and being part of a team that is revolutionizing pet health. I am ready to relocate and work hybrid from your Midtown Manhattan office.

Thank you for considering my application. I would love to discuss how my React and TypeScript experience, combined with my enthusiasm for learning NextJS and e-commerce development, can contribute to Spot \& Tango's mission.

\vspace{8pt}

\noindent
Sincerely,\\[8pt]
Yosr Ben Nagra

\end{document}
