\documentclass[11pt,a4paper]{article}
\input{../preamble}

\cvname{Yosr Ben Nagra}
\cvrole{Full Stack Developer}
\cvcontact{Ariana, Tunisia}
\cvphone{+216 53916040}
\cvemail{yosrbennagra@gmail.com}
\cvaddress{Ariana, Tunisia}
\cvgithub{https://github.com/YosrBennagra}
\cvwebsite{https://portfolio-yosr.vercel.app/en}

\begin{document}
\makecvheader
\makecontactinfo

\vspace{12pt}

\noindent Dear Hiring Team,

I am writing to express my strong interest in the Full Stack Developer position at your company. As a passionate developer with hands-on experience in building scalable web applications using React, NestJS, and modern cloud technologies, I am excited about the possibility of contributing to your engineering team.

Throughout my academic and professional journey, I have developed a deep expertise in the JavaScript ecosystem. My recent experience includes designing and implementing full-stack platforms integrating AI and DevOps practices. At IT Serv, I built a comprehensive healthcare platform using React and Flask, where I not only developed the core features but also set up CI/CD pipelines with Jenkins and Docker to ensure reliable deployments. This experience taught me the value of owning the entire development lifecycle, from architecture design to production monitoring.

I pride myself on writing clean, maintainable code and building intuitive user interfaces. My background includes developing real-time collaboration tools using WebSockets and NestJS, as well as creating responsive educational platforms with React and TypeScript. I am proficient in both SQL and NoSQL databases (PostgreSQL, MongoDB) and have a strong grasp of testing methodologies using Jest and React Testing Library.

Beyond technical skills, I am a proactive learner who thrives in collaborative environments. I am accustomed to working in Agile teams, participating in code reviews, and communicating effectively with cross-functional stakeholders. I am particularly drawn to companies that value innovation and technical excellence, and I am eager to bring my problem-solving skills and dedication to quality to your projects.

I am confident that my technical background in full-stack development, combined with my enthusiasm for learning new technologies, would make me a valuable addition to your team. I look forward to the opportunity to discuss how my skills and experience align with your needs.

Thank you for your time and consideration.

\vspace{6pt}
\noindent Best regards,\\
\textbf{Yosr Ben Nagra}

\end{document}
