% Twitch Software Development Engineer - Video Platform
% Yosr Ben Nagra

\documentclass[11pt,a4paper]{article}
\usepackage[margin=1in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}

\setlength{\parindent}{0pt}
\setlength{\parskip}{10pt}

\begin{document}

\begin{center}
\textbf{\Large Yosr Ben Nagra}\\
yosrbennagra@gmail.com | +216 53916040\\
\href{https://github.com/YosrBennagra}{github.com/YosrBennagra} | \href{https://portfolio-yosr.vercel.app/en}{portfolio-yosr.vercel.app}
\end{center}

\vspace{10pt}

Twitch Hiring Team\\
Video Platform Team\\

Dear Hiring Manager,

I'm excited to apply for the Software Development Engineer position on Twitch's Video Platform team. As a final-year Computer Science student at ESPRIT with hands-on experience building scalable full-stack platforms and a passion for live streaming communities, I'm eager to contribute to delivering exceptional video experiences for millions of Creators and Viewers worldwide.

\textbf{Technical Qualifications:}

\begin{itemize}[leftmargin=*, itemsep=2pt]
    \item \textbf{Modern Development:} Strong proficiency in TypeScript/React (built collaborative platform and educational apps), with additional experience in Python, C++, and Java across full-stack projects
    \item \textbf{Backend Systems:} Developed RESTful APIs using NestJS, Flask, and Spring Boot; designed data models for MongoDB, PostgreSQL, and Oracle databases
    \item \textbf{Cloud \& DevOps:} Hands-on with Docker containerization, CI/CD pipelines (Jenkins, GitHub Actions), and cloud-native architecture principles
    \item \textbf{Algorithms \& Data Structures:} Strong foundation through academic projects (C++ Construction Management System, algorithmic problem-solving) and real-world applications
\end{itemize}

\textbf{Relevant Experience:}

At IT Serv, I'm building an AI-powered healthcare platform integrating video consultation capabilities, real-time features, and scalable backend services. I've gained experience with performance optimization, API design, and ensuring smooth user experiences at scale. Previously at IronByte and Ooredoo Tunisie, I developed real-time communication features and collaborated across product, design, and engineering teams.

\textbf{Why Twitch:}

I've been a Twitch viewer for years, following gaming streams and creative communities. I'm energized by the challenge of building systems that empower millions of live interactions daily. The opportunity to work on video delivery infrastructure that directly impacts Creator success and Viewer engagement aligns perfectly with my goal of building technology that strengthens communities.

I'm ready to relocate to San Francisco or Irvine and contribute to Twitch's engineering culture through collaboration, problem-solving, and continuous learning. While I'm eager to deepen my knowledge of video delivery systems and AWS Interactive Video Service, my track record of rapidly adopting new technologies positions me to make meaningful contributions quickly.

Thank you for considering my application. I'd love to discuss how my full-stack development experience and passion for live streaming can contribute to Twitch's Video Platform team.

\vspace{10pt}

Best regards,\\
Yosr Ben Nagra

\end{document}
