\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{times}
\usepackage[english]{babel}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\usepackage{parskip}
\usepackage{enumitem}

\hypersetup{
  colorlinks=true,
  urlcolor=black,
  linkcolor=black
}

\pagestyle{empty}

\begin{document}

\begin{flushleft}
\textbf{Yosr Ben Nagra}\\
+216 53916040\\
\href{mailto:yosrbennagra@gmail.com}{yosrbennagra@gmail.com}\\
\href{https://portfolio-yosr.vercel.app/en}{portfolio-yosr.vercel.app}\\
\href{https://github.com/YosrBennagra}{github.com/YosrBennagra}\\
Ariana, Tunisia
\end{flushleft}

\vspace{0.5cm}

\begin{flushleft}
\today
\end{flushleft}

\vspace{0.5cm}

\begin{flushleft}
\textbf{Subject: Application for Full Stack Developer Position -- Multi-Agent Solutions at EY}
\end{flushleft}

\vspace{0.5cm}

Dear Hiring Manager,

I am a Software Engineer with hands-on experience building full-stack web applications and integrating AI-powered solutions. I am excited about the opportunity to contribute to EY's multi-agent platform development.

During my recent work at IT Serv, I designed and developed a full-stack healthcare platform using React for the frontend and Flask (Python) for the backend. I integrated AI functionalities using Hugging Face models, built RESTful APIs connecting the frontend to AI-powered features, and established CI/CD pipelines with Docker and Jenkins. This experience aligns closely with building user-facing interfaces for AI agent interactions and backend services.

My technical background includes:

\begin{itemize}[leftmargin=15pt]
  \item React, TypeScript, and Node.js (NestJS) for modern web interfaces
  \item Python (Flask) and RESTful/GraphQL API development
  \item Experience integrating AI models with web applications
  \item CI/CD implementation and secure deployment practices
  \item Database management (MongoDB, PostgreSQL, MySQL)
\end{itemize}

At IronByte, I developed a full-stack educational platform with NestJS and React, implementing secure authentication and authorization. At Ooredoo Tunisie, I built an internal communication application with Spring Boot and Angular, delivering UX/UI design and comprehensive testing.

While I have strong cloud fundamentals through my work with Docker, CI/CD pipelines, and deployment automation, I am eager to deepen my expertise in Azure services and would bring a quick learning ability and strong problem-solving skills to master Azure App Services, Functions, and authentication systems.

I am proficient in English and French, with excellent collaboration skills developed through agile team environments. I would be thrilled to contribute to building secure, scalable solutions for EY's internal multi-agent platform.

Thank you for considering my application. I look forward to discussing how my experience can contribute to EY's team.

Best regards,

\vspace{0.5cm}

Yosr Ben Nagra

\end{document}
