\documentclass[11pt,a4paper]{article}
\input{../preamble}

\begin{document}

\begin{center}
    {\LARGE Cover Letter}\\[4pt]
    {\large Fullstack Developer}
\end{center}
\vspace{10pt}

Ariana, Tunisia\\
November 25, 2025\\[6pt]

Hiring Team\\
Click\&Boat\\
Paris, France\\[10pt]

Dear Hiring Team,

I am writing to express my strong interest in the Fullstack Developer position at Click\&Boat. As a recently graduated full-stack engineer with experience building React, Angular, and backend services across Python, Java, and Node.js, I am excited by the opportunity to join a product-focused, data-driven team that empowers developers to shape company strategy. Click\&Boat's mission to make boating accessible worldwide and your innovative working culture—where developers are strategic partners, not just coders—aligns perfectly with how I approach software development.

Throughout my internships at IT Serv, IronByte, and Ooredoo, I have embraced a full-stack mindset, working across frontend interfaces, backend APIs, databases, and deployment pipelines. At IT Serv, I designed and implemented a healthcare platform using React, Flask, and MongoDB, integrating AI-powered features and setting up CI/CD with Docker and Jenkins. At IronByte, I built an educational web application with React and NestJS (TypeScript), focusing on clean architecture and user-centered solutions. Earlier, at Ooredoo, I developed an internal communication tool using Angular and Spring Boot (Java), implementing real-time chat features and writing comprehensive unit and integration tests. Across these experiences, I collaborated closely with product managers and designers to understand user needs, prepared features from concept to production, and monitored deployments to ensure reliability.

While my current stack includes React, Angular, Spring Boot, Flask, NestJS, and MySQL/MongoDB/PostgreSQL, I am eager to work with PHP, Symfony, and your Angular-based frontend. I believe in choosing the right tool for the job and value "boring architecture"—seeking the simplest solution to complex challenges. I am motivated by building products that solve real problems for end users, not just creating nice tech for its own sake. I am curious, business-oriented, and thrive in environments with high ownership and fast iteration. I want to contribute to Click\&Boat's product roadmap, participate in data-driven decisions, and help deliver exceptional experiences to boat owners and renters around the world.

What excites me most about Click\&Boat is the full transparency, empowerment, and collaborative culture you've built. The opportunity to work closely with talented engineers from Doctolib and ManoMano, take ownership of projects quickly, and push to production twice a day is exactly the kind of environment where I learn and grow best. I am committed to understanding your customers deeply and fully embracing your mission to make boating accessible globally.

You can explore my projects, technical background, and live demos in my online portfolio: \url{https://portfolio-yosr.vercel.app/en}.

Thank you for considering my application. I would welcome the opportunity to discuss how my full-stack experience, collaborative mindset, and eagerness to learn PHP/Symfony can help Click\&Boat continue building world-class products that transform the boating industry.

Sincerely,\\[4pt]
Yosr Ben Nagra

\end{document}
