\documentclass[11pt,a4paper]{article}
\input{../preamble}

\begin{document}

\begin{center}
    {\LARGE Cover Letter}\\[4pt]
    {\large Frontend Engineer}
\end{center}
\vspace{10pt}

Ariana, Tunisia\\
November 25, 2025\\[6pt]

Hiring Team\\
Sysdig\\
United States\\[10pt]

Dear Hiring Team,

I am writing to express my strong interest in the Frontend Engineer position at Sysdig. As a recently graduated full-stack engineer with hands-on experience building React and TypeScript single-page applications, I am excited by the opportunity to contribute to cloud security solutions that protect some of the world's most innovative organizations. Sysdig's mission to secure innovation in the cloud resonates deeply with me, and I would be proud to help build the elegant, performant user interfaces that make your security platform accessible and trustworthy.

Throughout my internships at IT Serv, IronByte, and Ooredoo, I have focused on delivering responsive, data-driven interfaces using modern frameworks. At IT Serv, I built React components for an AI-powered healthcare platform, working closely with backend Flask services and MongoDB. I containerized the application with Docker and set up CI/CD pipelines using Jenkins, gaining direct experience with the deployment workflows that are essential in cloud environments. At IronByte, I developed features for an educational web application using React and NestJS with TypeScript, focusing on clean component architecture and real-time collaboration. Earlier, at Ooredoo, I contributed to an internal communication tool built with Angular and Spring Boot, where I collaborated on UX/UI design and wrote unit and integration tests to ensure reliability.

Beyond my internship work, I have built a collaborative document platform using React, TypeScript, NestJS, and WebSockets, implementing real-time editing features and deploying the application with GitHub Actions and Vercel. This project taught me the importance of performance optimization, testing with Jest and React Testing Library, and designing interfaces that scale gracefully under load. I am comfortable working with modern browser APIs, component libraries, and shared design systems, and I enjoy the challenge of balancing functionality with user experience.

What draws me to Sysdig is your commitment to open innovation and your leadership in cloud-native security. I have followed Falco's impact on the cloud security ecosystem, and I am eager to learn more about container and Kubernetes security concepts as I grow with your team. I thrive in collaborative, cross-functional environments where honesty, integrity, and open communication drive better outcomes. I believe my frontend skills, combined with my experience in API integration, containerization, and CI/CD, position me well to contribute to your mission from day one.

You can explore my projects, technical background, and live demos in my online portfolio: \url{https://portfolio-yosr.vercel.app/en}.

Thank you for considering my application. I would welcome the opportunity to discuss how my experience building modern web applications, working with Docker and cloud deployment pipelines, and collaborating across product and engineering teams can help Sysdig deliver best-in-class security solutions to your customers.

Sincerely,\\[4pt]
Yosr Ben Nagra

\end{document}
