\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{times}
\usepackage[english]{babel}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\usepackage{parskip}
\usepackage{enumitem}

\hypersetup{
  colorlinks=true,
  urlcolor=black,
  linkcolor=black
}

\pagestyle{empty}

\begin{document}

\begin{flushleft}
\textbf{Yosr Ben Nagra}\\
+216 53916040\\
\href{mailto:yosrbennagra@gmail.com}{yosrbennagra@gmail.com}\\
\href{https://portfolio-yosr.vercel.app/en}{portfolio-yosr.vercel.app}\\
\href{https://github.com/YosrBennagra}{github.com/YosrBennagra}\\
Ariana, Tunisia
\end{flushleft}

\vspace{0.5cm}

\begin{flushleft}
\today
\end{flushleft}

\vspace{0.5cm}

\begin{flushleft}
\textbf{Subject: Application for Junior Software Developer Position (Remote)}
\end{flushleft}

\vspace{0.5cm}

Dear Hiring Manager,

I am a Software Engineer with hands-on experience building, testing, and maintaining full-stack applications. I am excited about this remote Junior Software Developer opportunity and eager to contribute clean, efficient code while continuously learning and growing.

\textbf{Technical Foundation}

\begin{itemize}[leftmargin=15pt, itemsep=2pt]
  \item \textbf{Programming Languages:} Proficient in JavaScript, TypeScript, Python, Java, C++, C\#
  \item \textbf{Software Development Fundamentals:} Strong understanding of OOP, data structures, and algorithms from Bachelor's degree in Computer Science
  \item \textbf{Version Control:} Experienced with Git and GitHub, including code reviews and collaborative workflows
  \item \textbf{Web Technologies:} Backend (Node.js, NestJS, Express, Flask, Spring Boot) and Frontend (React, Angular)
  \item \textbf{APIs \& Databases:} RESTful APIs, GraphQL, MongoDB, PostgreSQL, MySQL, Oracle, SQL Server
  \item \textbf{Testing \& Quality:} Unit testing, integration testing with Jest and JUnit
\end{itemize}

\textbf{Proven Software Development Experience}

\textit{IT Serv (Feb 2025 - Aug 2025) - Full-Stack Developer Intern}
\begin{itemize}[leftmargin=15pt, itemsep=2pt]
  \item Designed and developed full-stack web platform integrating AI, DevOps, and RAG
  \item Wrote clean, well-documented code for React frontend and Flask (Python) backend
  \item Debugged and resolved software defects across the application stack
  \item Set up CI/CD pipelines with Docker and Jenkins for reliable deployment
  \item Technologies: React, Flask, MongoDB, Python, Docker, Jenkins
\end{itemize}

\textit{IronByte (Jun 2024 - Aug 2024) - Full-Stack Developer Intern}
\begin{itemize}[leftmargin=15pt, itemsep=2pt]
  \item Developed educational web application with NestJS backend and React frontend
  \item Participated in code reviews to ensure quality and consistency
  \item Built new features including timetable creation tool improving scheduling efficiency
  \item Technologies: NestJS, React, MongoDB, TypeScript, JavaScript
\end{itemize}

\textit{Ooredoo Tunisie (Jul 2023 - Sep 2023) - Full-Stack Developer Intern}
\begin{itemize}[leftmargin=15pt, itemsep=2pt]
  \item Built internal communication app with real-time chat using Spring Boot and Angular
  \item Delivered UX/UI design and comprehensive unit/integration tests
  \item Collaborated with cross-functional teams for feature development
  \item Technologies: Spring Boot (Java), Angular
\end{itemize}

\textbf{Problem-Solving \& Collaboration}

I have strong analytical skills and a proven ability to debug complex issues across frontend, backend, and database layers. I've collaborated effectively with designers, QA, and product managers in agile environments. My experience with code reviews, Git workflows, and documentation ensures I contribute to maintainable, team-oriented codebases.

\textbf{Continuous Learning}

I'm passionate about learning new technologies and best practices. I've worked with diverse tech stacks (React, Angular, Node.js, Python, Java), always adapting quickly to project requirements. I understand the importance of security, performance, and scalability, and I'm eager to deepen my expertise in these areas.

\textbf{Portfolio}

Please visit \textbf{\href{https://portfolio-yosr.vercel.app/en}{portfolio-yosr.vercel.app}} and my \textbf{\href{https://github.com/YosrBennagra}{GitHub}} to see my projects, code quality, and technical range.

I am excited about joining your team remotely, contributing reliable and efficient solutions, and growing as a software developer. I am fluent in English, French, and Arabic, with strong communication skills for remote collaboration.

Thank you for considering my application. I look forward to discussing how I can contribute to your team.

Best regards,

\vspace{0.5cm}

Yosr Ben Nagra

\end{document}
