\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{times}
\usepackage[english]{babel}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\usepackage{parskip}
\usepackage{enumitem}

\hypersetup{
  colorlinks=true,
  urlcolor=black,
  linkcolor=black
}

\pagestyle{empty}

\begin{document}

\begin{flushleft}
\textbf{Yosr Ben Nagra}\\
+216 53916040\\
\href{mailto:yosrbennagra@gmail.com}{yosrbennagra@gmail.com}\\
\href{https://portfolio-yosr.vercel.app/en}{portfolio-yosr.vercel.app}\\
\href{https://github.com/YosrBennagra}{github.com/YosrBennagra}\\
Ariana, Tunisia
\end{flushleft}

\vspace{0.5cm}

\begin{flushleft}
\today
\end{flushleft}

\vspace{0.5cm}

\begin{flushleft}
\textbf{Subject: Application for UX/UI Designer Position at LINE MAN Wongnai}
\end{flushleft}

\vspace{0.5cm}

Dear Hiring Manager,

I am a Full-Stack Developer with strong UX/UI design experience, passionate about creating beautiful, intuitive interfaces that solve real user problems. I'm excited to shape the future of LINE MAN Wongnai's products and impact millions of users across Thailand.

\textbf{Experience Summary}

I bridge design vision and technical execution. Over three internships, I designed and built responsive web and mobile applications:

\begin{itemize}[leftmargin=15pt, itemsep=2pt]
  \item \textbf{IT Serv:} Designed React healthcare platform with intuitive interfaces for symptom checker, forums, and blogs
  \item \textbf{IronByte:} Built educational app with user-friendly flows and clean UX improving scheduling efficiency
  \item \textbf{Ooredoo:} Delivered complete UX/UI design for Angular communication app with chat, search, and filtering
\end{itemize}

\textbf{Design Skills}

\begin{itemize}[leftmargin=15pt, itemsep=2pt]
  \item User-centric design thinking and research-driven solutions
  \item Design principles mastery: layout, typography, spacing, hierarchy, accessibility
  \item Platform expertise: iOS, Android, and web—understanding limitations and patterns
  \item Pixel-perfect responsive design across mobile, tablet, desktop
  \item Data-driven iteration based on user feedback and analytics
\end{itemize}

\textbf{Technical Implementation}

Unlike pure designers, I implement my own designs with React, Angular, TypeScript, HTML5, CSS3. I create prototypes, build smooth animations, and work closely with engineers to ensure quality and feasibility.

\textbf{Collaboration \& Approach}

I work effectively with PMs, engineers, and stakeholders. I facilitate discussions, consolidate feedback, question requirements, and push for right UX outcomes with logical, data-driven arguments. I take ownership from research to delivery and participate in strategic product decisions.

\textbf{Portfolio}

Visit \textbf{\href{https://portfolio-yosr.vercel.app/en}{portfolio-yosr.vercel.app}} to see my responsive interfaces, user-centric solutions, and design system implementations.

\textbf{Why LINE MAN Wongnai}

I bring logic-driven problem-solving, passion for UI and technology, autonomous ownership, and eagerness to innovate with deep UX/UI knowledge (accessibility, animations, analytics). I'm excited to contribute to Thailand's No.1 food platform.

Thank you for considering my application. I look forward to discussing how I can create beautiful, intuitive experiences for your users.

Best regards,

\vspace{0.5cm}

Yosr Ben Nagra

\end{document}
