\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{times}
\usepackage[english]{babel}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\usepackage{parskip}
\usepackage{enumitem}

\hypersetup{
  colorlinks=true,
  urlcolor=black,
  linkcolor=black
}

\pagestyle{empty}

\begin{document}

\begin{flushleft}
\textbf{Yosr Ben Nagra}\\
+216 53916040\\
\href{mailto:yosrbennagra@gmail.com}{yosrbennagra@gmail.com}\\
\href{https://portfolio-yosr.vercel.app/en}{portfolio-yosr.vercel.app}\\
\href{https://github.com/YosrBennagra}{github.com/YosrBennagra}\\
Ariana, Tunisia
\end{flushleft}

\vspace{0.5cm}

\begin{flushleft}
\today
\end{flushleft}

\vspace{0.5cm}

\begin{flushleft}
\textbf{Subject: Application for Junior C/C++ RAN Telecom SW Engineer at Tietoevry}
\end{flushleft}

\vspace{0.5cm}

Dear Hiring Manager,

I am a Computer Science graduate with strong C/C++ programming skills and hands-on experience in Unix/Linux, Docker, CI/CD, and Python automation. I am excited to join Tietoevry's R\&D team and contribute to telecom software development.

\textbf{Technical Qualifications}

\begin{itemize}[leftmargin=15pt, itemsep=2pt]
  \item \textbf{C/C++ Knowledge:} Developed Construction Management System in C++ applying OOP principles; built Shape Blaster game with C\# (similar C-family language syntax and paradigms)
  \item \textbf{Unix/Linux:} Hands-on experience with Linux systems through Docker containerization and CI/CD pipeline deployment at IT Serv
  \item \textbf{Docker \& Kubernetes:} Set up Docker containers and CI/CD pipelines with Jenkins for production platform deployment
  \item \textbf{CI/CD Pipelines:} Built automated pipelines using Jenkins, GitHub Actions, and GitLab CI across multiple projects
  \item \textbf{Git/Gerrit:} Proficient with Git version control, GitHub workflows, and code review processes
  \item \textbf{Python Automation:} Developed Flask backend and automation scripts for testing and monitoring
  \item \textbf{CMake:} Familiar with build automation tools from academic and personal projects
\end{itemize}

\textbf{Experience \& Skills}

During my internships at IT Serv, IronByte, and Ooredoo, I worked on full-stack applications, debugged production issues, followed technical specifications, and collaborated with cross-functional teams. I have strong analytical and debugging skills, learn new technologies quickly, and bring creativity to problem-solving.

I hold a Bachelor's degree in Computer Science from ESPRIT and am fluent in English (Upper-Intermediate level). I'm eager to learn about radio networks, 3GPP specifications, and embedded systems development while contributing to your international telecom projects.

\textbf{Why Tietoevry}

I'm drawn to the opportunity to work on interesting international projects, develop my skills in a supportive environment, and contribute to cutting-edge telecom software. I value work-life balance, continuous learning, and diversity—all of which align with Tietoevry's culture.

Thank you for considering my application. I look forward to discussing how I can support your R\&D team.

Best regards,

\vspace{0.5cm}

Yosr Ben Nagra

\end{document}
