\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{times}
\usepackage[english]{babel}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\usepackage{parskip}
\usepackage{enumitem}

\hypersetup{
  colorlinks=true,
  urlcolor=black,
  linkcolor=black
}

\pagestyle{empty}

\begin{document}

\begin{flushleft}
\textbf{Yosr Ben Nagra}\\
+216 53916040\\
\href{mailto:yosrbennagra@gmail.com}{yosrbennagra@gmail.com}\\
\href{https://portfolio-yosr.vercel.app/en}{portfolio-yosr.vercel.app}\\
\href{https://github.com/YosrBennagra}{github.com/YosrBennagra}\\
Ariana, Tunisia
\end{flushleft}

\vspace{0.5cm}

\begin{flushleft}
\today
\end{flushleft}

\vspace{0.5cm}

\begin{flushleft}
\textbf{Subject: Application for Senior Frontend Developer Position at TRVL Code}
\end{flushleft}

\vspace{0.5cm}

Dear TRVL Code Team,

I am a Frontend Developer with a falcon-eye for UI detail and a passion for building pixel-perfect, mobile-first experiences that go beyond mockups. I don't just execute designs-I elevate them.

\textbf{Mobile-First Mastery}

I fully understand the distinctions between responsive design (fluid grids), adaptive design (breakpoint-specific layouts), and dedicated mobile versions (different UI patterns for B2C). My approach: start mobile-first, analyze designs critically, propose UX improvements, and deliver native-feeling experiences.

\textbf{Technical Expertise}

\begin{itemize}[leftmargin=15pt, itemsep=2pt]
  \item React, Next.js, TypeScript with SSR/SSG
  \item CSS mastery: flexbox, grid, spacing systems, typography-not just framework reliance
  \item Cross-browser pixel-perfect debugging (Chrome, Safari, Firefox, Edge, iOS, Android)
  \item Performance optimization, Web Vitals, accessibility
\end{itemize}

\textbf{Proven UI Engineering}

At IT Serv, I built a React healthcare platform with responsive dashboards and patient forums. At IronByte, I developed an educational platform with intuitive interfaces. Every project: pixel-perfect implementation, smooth animations, mobile-optimized layouts, clean component architecture.

\textbf{Portfolio}

Please explore \textbf{\href{https://portfolio-yosr.vercel.app/en}{portfolio-yosr.vercel.app}} to see my responsive/adaptive layouts, modern design implementation, and TypeScript component architecture.

\textbf{Why TRVL Code}

I'm committed full-time to building exceptional interfaces. I'm detail-obsessed (notice 1px misalignments), perfection-driven, proactive, mobile-first native, and solution-oriented. I think in mobile constraints first and propose improvements when I see opportunities.

I'm excited about building high-impact B2C travel experiences where every pixel matters.

Thank you for considering my application. I look forward to discussing how I can contribute to TRVL Code's vision.

Best regards,

\vspace{0.5cm}

Yosr Ben Nagra

\end{document}
