\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{times}
\usepackage[english]{babel}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\usepackage{parskip}
\usepackage{enumitem}

\hypersetup{
  colorlinks=true,
  urlcolor=black,
  linkcolor=black
}

\pagestyle{empty}

\begin{document}

\begin{flushleft}
\textbf{Yosr Ben Nagra}\\
+216 53916040\\
\href{mailto:yosrbennagra@gmail.com}{yosrbennagra@gmail.com}\\
\href{https://portfolio-yosr.vercel.app/en}{portfolio-yosr.vercel.app}\\
\href{https://github.com/YosrBennagra}{github.com/YosrBennagra}\\
Ariana, Tunisia
\end{flushleft}

\vspace{0.5cm}

\begin{flushleft}
\today
\end{flushleft}

\vspace{0.5cm}

\begin{flushleft}
\textbf{Subject: Application for Junior Software Developer Position at Decisions}
\end{flushleft}

\vspace{0.5cm}

Dear Hiring Manager,

I am a recent Computer Science graduate eager to launch my career in .NET and C\# development at Decisions. I'm passionate about building real-world applications, learning modern development practices, and contributing to your business process automation platform.

\textbf{Technical Foundation}

I have hands-on experience with the technologies Decisions uses:

\begin{itemize}[leftmargin=15pt, itemsep=2pt]
  \item \textbf{React, HTML5, CSS, JavaScript:} Built production web applications at IT Serv and IronByte with React frontends
  \item \textbf{C\#:} Developed Shape Blaster, a 2D puzzle game using Unity and C\#, applying OOP principles for game mechanics
  \item \textbf{Object-Oriented Programming:} Strong foundation from bachelor's degree and multiple projects using OOP in C\#, C++, Java, and TypeScript
  \item \textbf{ASP.NET knowledge:} Familiar with MVC patterns through academic training and full-stack development experience
  \item \textbf{Docker \& CI/CD:} Set up containerization and continuous integration pipelines at IT Serv using Docker and Jenkins
\end{itemize}

\textbf{Real-World Software Development}

\textit{IT Serv (Feb 2025 - Aug 2025) - Full-Stack Developer Intern}

Designed and developed a full-stack healthcare platform with React frontend and Python backend. Integrated AI features, implemented RESTful APIs, and established CI/CD pipelines with Docker and Jenkins. Collaborated in an agile environment with product managers and designers.

\textit{IronByte (Jun 2024 - Aug 2024) - Full-Stack Developer Intern}

Built an educational web application using React and NestJS (Node.js + TypeScript). Developed features including assignment submission, lesson sharing, and a timetable creation tool. Participated in code reviews and agile sprint planning.

\textit{Ooredoo Tunisie (Jul 2023 - Sep 2023) - Full-Stack Developer Intern}

Created an internal communication application with Spring Boot (Java) and Angular. Delivered UX/UI design and comprehensive unit/integration testing. Worked within SDLC practices and met project deadlines effectively.

\textbf{Project Portfolio}

\begin{itemize}[leftmargin=15pt, itemsep=2pt]
  \item \textbf{Shape Blaster (C\# / Unity):} Mobile game demonstrating OOP design, data structures, and problem-solving
  \item \textbf{Collaborative Platform (React / TypeScript / NestJS):} Real-time document sharing with WebSockets and CI/CD
  \item \textbf{Construction Management System (C++):} Desktop application with database management and business logic
\end{itemize}

View my portfolio at \textbf{\href{https://portfolio-yosr.vercel.app/en}{portfolio-yosr.vercel.app}} and GitHub at \textbf{\href{https://github.com/YosrBennagra}{github.com/YosrBennagra}}.

\textbf{Why I'm a Great Fit}

\begin{itemize}[leftmargin=15pt, itemsep=2pt]
  \item \textbf{Fresh graduate ready to learn:} Bachelor's in Computer Science (ESPRIT), graduated June 2025
  \item \textbf{Hands-on experience:} Three internships building production software in agile environments
  \item \textbf{Strong OOP foundation:} Applied across C\#, Java, C++, and TypeScript projects
  \item \textbf{Analytical mindset:} Solved complex technical challenges across frontend, backend, and integration
  \item \textbf{Collaborative spirit:} Worked effectively with cross-functional teams, participated in code reviews
  \item \textbf{Eager to contribute:} Ready to build business automation solutions and grow in a .NET environment
\end{itemize}

I'm excited about joining Decisions to work with ASP.NET MVC, C\#, React, and Docker while learning from senior engineers through structured mentorship. I thrive in collaborative environments, meet deadlines consistently, and take initiative to solve problems.

I am available for the Mumbai position and committed to the 11:00 AM - 8:00 PM schedule. Thank you for considering my application. I look forward to discussing how I can contribute to Decisions' platform and grow as a developer.

Best regards,

\vspace{0.5cm}

Yosr Ben Nagra

\end{document}
