\documentclass[11pt,a4paper]{article}
\input{../preamble}

\cvname{Yosr Ben Nagra}
\cvrole{Software Engineer}
\cvcontact{Ariana, Tunisia}
\cvphone{+216 53916040}
\cvemail{yosrbennagra@gmail.com}
\cvaddress{Ariana, Tunisia}
\cvgithub{https://github.com/YosrBennagra}
\cvwebsite{https://portfolio-yosr.vercel.app/en}

\begin{document}
\makecvheader
\makecontactinfo

\vspace{12pt}

\noindent Dear Just Hiring Team,

I'm excited to apply for the Software Engineer position at Just. Your mission to help people achieve a better later life resonates deeply with me. Retirement should be a time of security and enjoyment, not stress and uncertainty. The opportunity to contribute to market-leading retirement solutions through modern engineering practices is exactly the kind of purposeful work I'm looking for.

I bring hands-on experience building full-stack applications with React TypeScript and Python. At IronByte, I developed an educational platform using React and TypeScript, implementing complex state management and reusable components for assignment submission and scheduling features. At IT Serv, I built a Python Flask backend with RESTful APIs serving a React frontend, handling everything from database design (MongoDB) to CI/CD pipeline setup with Jenkins and Docker containerization. This cross-stack experience has taught me how to design APIs that frontend teams love and build UIs that make backend integration seamless.

I'm comfortable with the core technologies in your stack. I've worked extensively with React (including Hooks and Context API), TypeScript, and Python, and I've deployed containerized applications with Docker and automated builds through CI/CD pipelines. While I haven't worked with Next.js specifically, I understand it's a React framework with server-side rendering and static generation, concepts I'm eager to learn and apply. Similarly, while my Python API experience is with Flask, I'm confident I can quickly adapt to FastAPI given their similar design philosophies.

I want to be transparent: my experience has been primarily with on-premises and basic cloud deployments rather than Azure-specific services like AKS, Key Vault, or Azure DevOps. However, I have strong fundamentals in containerization (Docker), CI/CD automation (Jenkins, GitHub Actions), and infrastructure-as-code concepts. I'm a fast learner who thrives on picking up new tools and platforms. When I joined IT Serv, I had no AI/ML experience but successfully fine-tuned LLMs and implemented RAG pipelines within weeks. I'd approach Azure and Terraform with the same curiosity and determination.

What excites me about this role is the combination of technical depth and meaningful impact. Building a service-oriented data platform in a regulated environment requires careful attention to security, reliability, and scalability, exactly the kind of engineering challenges I enjoy. The emphasis on DevOps excellence, code reviews, and automated testing aligns perfectly with how I believe software should be built. And knowing that this work directly contributes to helping retirees achieve financial security makes it all the more rewarding.

I'm collaborative, curious, and committed to continuous improvement. I ask questions when I don't understand something, I learn from incident post-mortems, and I genuinely care about code quality and team velocity. I'd love to contribute to Just's growth journey and help build solutions that make a real difference in people's lives.

Thank you for considering my application. I'd welcome the opportunity to discuss how my full-stack experience and eagerness to learn can support the DB Transformation engineering team.

\vspace{6pt}
\noindent Best regards,\\
\textbf{Yosr Ben Nagra}

\end{document}
