\documentclass[11pt,a4paper]{article}
\input{../preamble}

\cvname{Yosr Ben Nagra}
\cvrole{Java Developer}
\cvcontact{Ariana, Tunisia}
\cvphone{+216 53916040}
\cvemail{yosrbennagra@gmail.com}
\cvaddress{Ariana, Tunisia}
\cvgithub{https://github.com/YosrBennagra}
\cvwebsite{https://portfolio-yosr.vercel.app/en}

\begin{document}
\makecvheader
\makecontactinfo

\vspace{12pt}

\noindent Dear Full Scale Hiring Team,

I'm excited to apply for the Java Developer position at Full Scale. As a software engineer who's built enterprise applications with Java and Spring Boot, I'm drawn to Full Scale's reputation for delivering high-quality digital solutions and working with clients worldwide.

At Ooredoo Tunisie, I developed an internal communication application using Spring Boot and Java, building RESTful APIs for real-time chat, user filtering, and search functionality. I worked with Oracle databases, handled complex SQL queries, and ensured data integrity across the system. I also delivered unit and integration tests to maintain code quality and collaborated with UX/UI designers to create intuitive interfaces, experience that aligns well with Full Scale's cross-functional team environment.

I understand object-oriented programming principles and have experience with the full development lifecycle: designing scalable systems, writing clean code, participating in code reviews, and debugging production issues. At IronByte, I built a full-stack educational platform with NestJS and React, integrating complex scheduling logic and assignment submission workflows. This required careful API design, database optimization, and close collaboration with team members, similar to the collaborative, fast-paced environment at Full Scale.

I'm comfortable working across the stack. While my Java experience is strong, I've also worked extensively with frontend technologies like React, TypeScript, and Angular, which helps me understand the complete picture when building APIs and services. I've worked with MySQL, PostgreSQL, MongoDB, and Oracle databases, and I'm familiar with CI/CD pipelines through Jenkins and GitHub Actions.

What excites me about this role is the opportunity to work on diverse projects for clients worldwide while growing as a Java developer. I'm eager to contribute to Full Scale's innovative solutions, stay current with emerging technologies, and collaborate with a talented team in a remote environment.

I'd love to discuss how my experience building Java-based applications, working with databases, and collaborating across teams can contribute to Full Scale's continued success.

Thank you for considering my application.

\vspace{6pt}
\noindent Best regards,\\
\textbf{Yosr Ben Nagra}

\end{document}
