\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{times}
\usepackage[english]{babel}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\usepackage{parskip}
\usepackage{enumitem}

\hypersetup{
  colorlinks=true,
  urlcolor=black,
  linkcolor=black
}

\pagestyle{empty}

\begin{document}

\begin{flushleft}
\textbf{Yosr Ben Nagra}\\
+216 53916040\\
\href{mailto:yosrbennagra@gmail.com}{yosrbennagra@gmail.com}\\
\href{https://portfolio-yosr.vercel.app/en}{portfolio-yosr.vercel.app}\\
\href{https://github.com/YosrBennagra}{github.com/YosrBennagra}\\
Ariana, Tunisia
\end{flushleft}

\vspace{0.5cm}

\begin{flushleft}
\today
\end{flushleft}

\vspace{0.5cm}

\begin{flushleft}
\textbf{Subject: Application for Junior Application Support Engineer Position at Tradeweb}
\end{flushleft}

\vspace{0.5cm}

Dear Hiring Manager,

I am a Computer Science graduate with hands-on experience in application support, production troubleshooting, and automation. I am excited about joining Tradeweb's Application Support team to provide technical support for your fixed income trading platform and gain deep expertise in the retail market technology stack.

\textbf{Technical Qualifications}

I have strong foundations in the technologies Tradeweb uses:

\begin{itemize}[leftmargin=15pt, itemsep=2pt]
  \item \textbf{Java \& Object-Oriented Programming:} Built production applications with Java (Spring Boot) at Ooredoo Tunisie
  \item \textbf{Scripting:} Proficient in Python and Bash for automation, monitoring, and task scripting
  \item \textbf{Relational Databases:} Experience with Oracle, PostgreSQL, MySQL—writing SQL queries and managing database operations
  \item \textbf{Unix/Linux Systems:} Comfortable with Unix command-line tools and shell scripting
  \item \textbf{CI/CD Systems:} Hands-on experience with GitLab CI/CD, GitHub Actions, Bamboo, and Jenkins
  \item \textbf{Application Servers:} Familiar with Apache Tomcat and HTTP server configurations
\end{itemize}

\textbf{Application Support Experience}

\textit{IT Serv (Feb 2025 - Aug 2025)}

Provided application-level support for a production healthcare platform. Diagnosed and resolved technical issues across the full stack. Set up CI/CD pipelines with Docker and Jenkins for automated deployments. Developed Python automation scripts for system monitoring and maintenance tasks. Worked closely with business and technical teams to analyze requirements and implement solutions.

\textit{IronByte (Jun 2024 - Aug 2024)}

Maintained and troubleshot a production educational platform. Worked with MongoDB database and RESTful APIs. Collaborated with QA and development teams in an agile environment to resolve platform issues and deploy new features. Applied object-oriented programming principles for clean, maintainable code.

\textit{Ooredoo Tunisie (Jul 2023 - Sep 2023)}

Built internal communication application using Java (Spring Boot) with Oracle database. Performed comprehensive unit and integration testing to ensure application stability. Supported deployment activities and resolved technical issues. Collaborated with business stakeholders to understand requirements and deliver solutions.

\textbf{Why I'm a Strong Fit}

\begin{itemize}[leftmargin=15pt, itemsep=2pt]
  \item \textbf{Problem-solving mindset:} Strong analytical skills demonstrated through diagnosing production issues across frontend, backend, and database layers
  \item \textbf{Team collaboration:} Worked effectively with QA, development, and business teams in fast-paced agile environments
  \item \textbf{Automation focus:} Built Python and Bash scripts to automate repetitive tasks and improve efficiency
  \item \textbf{Detail-oriented:} Thorough approach to testing, documentation, and code quality
  \item \textbf{Adaptable:} Quick learner comfortable with new technologies and platforms
  \item \textbf{Communication skills:} Clear verbal and written communication with technical and non-technical stakeholders
  \item \textbf{Availability:} Willing to work evenings/weekends for production deployments and support needs
\end{itemize}

\textbf{Understanding of the Role}

I understand the Application Support Engineer role requires being the central point of contact for technical platform support, working closely with development and QA teams, and facilitating production issue resolution. I'm excited to gain a well-rounded understanding of the retail fixed income marketplace while contributing to platform stability and customer satisfaction.

I am comfortable with remote work and can travel to the Jersey City office for team meetings and collaboration as needed. My strong organizational skills, ability to work under pressure, and commitment to providing high-level service make me well-suited for this role.

Thank you for considering my application. I look forward to discussing how I can contribute to Tradeweb's Application Support team and grow as an engineer within your technology organization.

Best regards,

\vspace{0.5cm}

Yosr Ben Nagra

\end{document}
