\documentclass[11pt,a4paper]{article}
\usepackage[margin=1in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\begin{document}

\begin{flushleft}
\textbf{Yosr Ben Nagra}\\
Ariana, Tunisia\\
+216 53916040\\
\href{mailto:yosrbennagra@gmail.com}{yosrbennagra@gmail.com}\\
\href{https://github.com/YosrBennagra}{github.com/YosrBennagra} | \href{https://portfolio-yosr.vercel.app/en}{portfolio-yosr.vercel.app}
\end{flushleft}

\vspace{10pt}

\noindent December 4, 2025

\vspace{10pt}

\noindent Thinkingbox\\
Brand Experience Agency\\

\vspace{10pt}

\noindent \textbf{RE: Application for Junior Front End Developer Position (3-Month Contract)}

\vspace{10pt}

Dear Hiring Team,

I am thrilled to apply for the Junior Front End Developer position at Thinkingbox. As a recent Computer Engineering graduate with hands-on experience building responsive web applications using React, HTML5, CSS3, and JavaScript, I'm excited about the opportunity to contribute to your agency's mission of creating innovative brand experiences while learning from your experienced development team.

\textbf{Technical Foundation \& Front End Expertise}

My background demonstrates strong proficiency in the core technologies and frameworks you seek:

\begin{itemize}[leftmargin=15pt, itemsep=2pt]
    \item \textbf{React Development:} Built multiple production-ready applications including a Notion-like collaborative document platform with real-time features, and an educational web application at IronByte. Currently developing interactive user interfaces at IT Serv using React and TypeScript.
    \item \textbf{HTML5, CSS3 \& JavaScript:} Extensive experience creating responsive, visually appealing interfaces with cross-browser compatibility. Skilled in modern JavaScript (ES6+), TypeScript, and CSS frameworks for pixel-perfect implementations.
    \item \textbf{UI/UX Design Principles:} Delivered comprehensive UX/UI design and implementation at Ooredoo Tunisie, demonstrating understanding of user-centered design and visual hierarchy. My portfolio showcases attention to detail and design sensibility across diverse projects.
    \item \textbf{Performance \& Optimization:} Experienced in optimizing web applications for speed and scalability, implementing efficient rendering strategies, and ensuring seamless functionality across devices and browsers.
\end{itemize}

\textbf{Collaborative Development \& Problem-Solving}

Throughout my internships at IT Serv, IronByte, and Ooredoo Tunisie, I've thrived in collaborative environments working alongside designers, backend developers, and product stakeholders. I excel at translating creative concepts into engaging user experiences—whether implementing AI-powered interfaces, real-time collaboration features, or intuitive educational platforms. My strong problem-solving skills, attention to detail, and curiosity drive me to explore creative solutions and continuously learn new approaches.

\textbf{Testing, Debugging \& Quality Assurance}

Quality is at the heart of my development process. I have extensive experience with:

\begin{itemize}[leftmargin=15pt, itemsep=2pt]
    \item Jest and React Testing Library for unit and integration testing
    \item Cross-browser testing and debugging to ensure seamless functionality
    \item Code reviews and collaborative debugging sessions with team members
    \item Version control with Git and GitHub for clean, maintainable codebases
\end{itemize}

\textbf{Continuous Learning \& Emerging Technologies}

I'm passionate about staying current with emerging trends in front end development. While I'm highly proficient in React, I'm eager to expand my knowledge of other frameworks like Vue.js and explore new tools and methodologies that Thinkingbox uses to push creative boundaries. My experience leveraging AI-assisted development tools (GitHub Copilot, ChatGPT) demonstrates my proactive approach to learning and enhancing productivity.

\textbf{Thriving in Fast-Paced Environments}

My experience managing multiple concurrent projects across internships has honed my ability to prioritize tasks, meet tight deadlines, and maintain high-quality output. I thrive in dynamic, fast-paced environments where creativity and collaboration fuel innovation. The opportunity to work in Thinkingbox's vibrant, collaborative culture—where craft, curiosity, and continuous learning are celebrated—aligns perfectly with my values and work style.

\textbf{Portfolio \& Work Examples}

My online portfolio (\href{https://portfolio-yosr.vercel.app/en}{portfolio-yosr.vercel.app}) showcases responsive web applications, interactive interfaces, and diverse technical projects that demonstrate my front end development capabilities and design sensibility. I invite you to explore my work and GitHub repositories to see examples of clean code, thoughtful UI implementation, and collaborative project contributions.

\textbf{Commitment \& Availability}

I am available to start immediately for the 3-month contract and am fully committed to delivering exceptional work while contributing positively to your team culture. I'm enthusiastic about the potential to convert this opportunity into a full-time role and grow with Thinkingbox long-term.

Thank you for considering my application. I would love the opportunity to discuss how my React expertise, collaborative spirit, and passion for creating engaging user experiences can contribute to Thinkingbox's innovative projects. I look forward to bringing fresh perspectives, creative energy, and technical skills to your team.

\vspace{10pt}

\noindent Sincerely,

\vspace{10pt}

\noindent Yosr Ben Nagra

\end{document}
